### 2013-01-20 Docs/visualization/visualization.tex
more details on python plotting scripts

{\tt AmrPostprocessing/F\_Src/python\_plotfile} provide a simple commandline
tool for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

@@

{\tt contourcompare.py} takes 2 plotfiles and a variable as arguments
and plots contours of the 2 datasets on the same set of axes.  This is 
form comparisons of different runs.  Running the script with no parameters
will give the full list available options.

@@

When writing a script to use in batch mode, one has to manually import
the import modules needed to work with \yt.  As such, all scripts must
import from the {\tt yt.mods} module, which is essentially a
convenience module that sets up the appropriate \yt namespace.  
%% As an aside, if you want to import a module as another variable in
%% the local namespace---e.g. {\tt import this.module as
%% local\_variable}---then this should be done via the various API's
%% for that particular piece of code.  For example,
For completeness, below is a script containing our example above.
\newpage
\begin{lstlisting}[language=Python]
# load our namespace
from yt.mods import *

>>>>

{\tt AmrPostprocessing/F\_Src/python\_plotfile} provide some simple commandline
tools for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

The path to {\tt fsnapshot.so} should be included in your {\tt PYTHONPATH}
environment variable.  This can be done by adding:
\begin{verbatim}
export PYTHONPATH="${PYTHONPATH}:/home/user/AmrPostprocessing/F_Src/python_plotfile}
\end{verbatim}
to your {\tt .bashrc}.

It is recommended that you use {\tt matplotlib} version 1.2.0 or
higher.  If the fonts look strange in the output files, you can try
installing the {\tt lyx-fonts} package and deleting your {\tt
  .matplotlib} directory, and trying again.

@@

{\tt contourcompare.py} takes two or three plotfiles and a single variable as arguments
and plots contours of the datasets on the same set of axes.  This is 
form comparisons of different runs.  Running the script with no parameters
will give the full list available options.

For example:
\begin{verbatim}
contourcompare.py tfromp plt00000 other_plt00000
\end{verbatim}
will make a contour plot of the variable {\tt tfromp} from the data in
{\tt plt00000} and {\tt other\_plt00000} shown on the same axes.

\subsection{\tt runtimevis.py}

The {\tt runtimevis.py} script is designed to be run from a submission
script to produce plots from plotfiles as they are produced.  This is
accomplished by hooking it into the {\tt process} scripts described in
Chapter~\ref{ch:managingjobs}.

The script itself reads in an inputs file, {\tt vis.in}, that
describes the variables to plot.  From 1 to 6 variables can be
plotting from a plotfile.  The script does its best to organize them
in columns and rows to maximize the plot area.  The image is always
output at 1280$\times$720 pixels, corresponding to 720p HD resolution.
For each variable, a block of the form:
\begin{verbatim}
[varname]
min = 1
max = 2
log = 1
\end{verbatim}
is supplied.  If {\tt min} or {\tt max} are omitted, then the data
limits are computed automatically.  If {\tt log} is omitted, then no
log is taken of the data before plotting.  The script is then run as:
\begin{verbatim}
runtimevis.py plt00000
\end{verbatim}

@@

When writing a script to use in batch mode, one has to manually import
the import modules needed to work with \yt.  As such, all scripts must
import from the {\tt yt.mods} module, which is essentially a
convenience module that sets up the appropriate \yt namespace.  
%% As an aside, if you want to import a module as another variable in
%% the local namespace---e.g. {\tt import this.module as
%% local\_variable}---then this should be done via the various API's
%% for that particular piece of code.  For example,
For completeness, below is a script containing our example above.
\begin{lstlisting}[language=Python]
# load our namespace
from yt.mods import *
